\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing income inequality with tax data - Switzerland from 1917 to 2010}

### 2014-12-23 paper/subdocuments/results.Rnw
93er punkt raus und names() zeile vertauscht

<<setup_data_Brühlhart with and without taxed>>=
# Ohne Nuller
bd <- read.csv("../../data/data_Schweiz.csv", header=TRUE,sep=";")
#Veranlagungsperiode -> Jahre
bd$Jahr <- as.numeric(substr(bd$Veranlagungsperiode,1,4))
bd$Jahr[nchar(as.character(bd$Veranlagungsperiode))>4] <- bd$Jahr[nchar(as.character(bd$Veranlagungsperiode))>4] - 2
bd<-bd %>% 
  filter(Einheit=="Total") %>% select(Veranlagungsperiode,Jahr,gini_steink,gini_steinka)
bd<-subset(bd,(Jahr<=1995 | Jahr >2002)&Veranlagungsperiode!=1995)
# 2011 zufügen
bd.2011 <- read.csv("../../data/NP_2011.csv",dec=",") %>% filter(Einheit=="Total") %>% mutate(Veranlagungsperiode=2011,Jahr=2011)%>% select(Veranlagungsperiode,Jahr,gini_steink,gini_steinka)
levels(bd$Veranlagungsperiode)<- c(levels(bd$Veranlagungsperiode),"2011")
bd <- rbind(bd,bd.2011[,names(bd)])
bd.long<-reshape(bd,
varying = c("gini_steink","gini_steinka"),
v.names = "Gini",
timevar = "inc_def",
times = c("taxable income (only taxed)","equivalised taxable income (only taxed)"),
direction ="long")
# mit Nuller
bd.0 <- read.csv("../../data/data_Schweiz_mitNull.csv", header=TRUE,sep=";")
#Veranlagungsperiode -> Jahre
bd.0$Jahr <- as.numeric(substr(bd.0$Veranlagungsperiode,1,4))
bd.0$Jahr[nchar(as.character(bd.0$Veranlagungsperiode))>4] <- bd.0$Jahr[nchar(as.character(bd.0$Veranlagungsperiode))>4] - 2
bd.0<-bd.0 %>% 
  filter(Einheit=="Total") %>% select(Veranlagungsperiode,Jahr,gini_steink,gini_steinka)
bd.0<-subset(bd.0,(Jahr<=1995 | Jahr >2002)&Veranlagungsperiode!=1995)
# 2011 zufügen
bd.0.2011 <- read.csv("../../data/NP_2011_mitnull.csv",dec=",") %>% filter(Einheit=="Total") %>% mutate(Veranlagungsperiode=2011,Jahr=2011) %>% select(Veranlagungsperiode,Jahr,gini_steink,gini_steinka)
levels(bd.0$Veranlagungsperiode)<- c(levels(bd.0$Veranlagungsperiode),"2011")
bd.0 <- rbind(bd.0,bd.0.2011[,names(bd.0)])
bd.0.long<-reshape(bd.0,
varying = c("gini_steink","gini_steinka"),
v.names = "Gini",
timevar = "inc_def",
times = c("taxable income","equivalised taxable income"),
direction ="long")
bdlong<-rbind(bd.0.long,bd.long)
names(bdlong)[3]<-"Income"
@

@@

estv_masse <- estv %>% 
  filter(kanton=="CH",
         eink_art=="Nach steuerbarem Einkommen",
         fall=="Normalfälle",
         anz_pflichtige>0) %>%
        # steuerperiode!=1945.5) %>% 
  select(bemessungsjahre, steink, kanton, eink_ll, eink_ul,anz_pflichtige) %>%
  group_by(factor(bemessungsjahre)) %>%
  mutate(mean_steink=steink/anz_pflichtige) %>%
  summarise(Gini=gini(mean_steink,weights=anz_pflichtige),Atkinson=getAtkinson(mean_steink,w=anz_pflichtige),Theil=getTheil(mean_steink,w=anz_pflichtige))
estv_masse$id<-1
estv_masse<-estv_masse[as.numeric(estv_masse$Year)>4,]

names(estv_masse)<-c("Year","Gini","Atkinson","Theil","id")
try(detach("package:reshape", unload=TRUE))
library(reshape2)
estv_masse_long <- melt(estv_masse,id=c("id","Year"))

>>>>

<<setup_data_Brühlhart with and without taxed>>=
# Ohne Nuller
bd <- read.csv("../../data/data_Schweiz.csv", header=TRUE,sep=";")
#Veranlagungsperiode -> Jahre
bd$Jahr <- as.numeric(substr(bd$Veranlagungsperiode,1,4))
bd$Jahr[nchar(as.character(bd$Veranlagungsperiode))>4] <- bd$Jahr[nchar(as.character(bd$Veranlagungsperiode))>4] - 2
bd<-bd %>% 
  filter(Einheit=="Total") %>% select(Veranlagungsperiode,Jahr,gini_steink,gini_steinka)
bd<-subset(bd,(Jahr<=1995 | Jahr >2002)&Veranlagungsperiode!=1995)
# 2011 zufügen
bd.2011 <- read.csv("../../data/NP_2011.csv",dec=",") %>% filter(Einheit=="Total") %>% mutate(Veranlagungsperiode=2011,Jahr=2011)%>% select(Veranlagungsperiode,Jahr,gini_steink,gini_steinka)
levels(bd$Veranlagungsperiode)<- c(levels(bd$Veranlagungsperiode),"2011")
bd <- rbind(bd,bd.2011[,names(bd)])
bd.long<-reshape(bd,
varying = c("gini_steink","gini_steinka"),
v.names = "Gini",
timevar = "inc_def",
times = c("taxable income (only taxed)","equivalised taxable income (only taxed)"),
direction ="long")
# mit Nuller
bd.0 <- read.csv("../../data/data_Schweiz_mitNull.csv", header=TRUE,sep=";")
#Veranlagungsperiode -> Jahre
bd.0$Jahr <- as.numeric(substr(bd.0$Veranlagungsperiode,1,4))
bd.0$Jahr[nchar(as.character(bd.0$Veranlagungsperiode))>4] <- bd.0$Jahr[nchar(as.character(bd.0$Veranlagungsperiode))>4] - 2
bd.0<-bd.0 %>% 
  filter(Einheit=="Total") %>% select(Veranlagungsperiode,Jahr,gini_steink,gini_steinka)
bd.0<-subset(bd.0,(Jahr==1995|Jahr>=2003)&Veranlagungsperiode!=1995)
# 2011 zufügen
bd.0.2011 <- read.csv("../../data/NP_2011_mitnull.csv",dec=",") %>% filter(Einheit=="Total") %>% mutate(Veranlagungsperiode=2011,Jahr=2011) %>% select(Veranlagungsperiode,Jahr,gini_steink,gini_steinka)
levels(bd.0$Veranlagungsperiode)<- c(levels(bd.0$Veranlagungsperiode),"2011")
bd.0 <- rbind(bd.0,bd.0.2011[,names(bd.0)])
bd.0.long<-reshape(bd.0,
varying = c("gini_steink","gini_steinka"),
v.names = "Gini",
timevar = "inc_def",
times = c("taxable income","equivalised taxable income"),
direction ="long")
bdlong<-rbind(bd.0.long,bd.long)
names(bdlong)[3]<-"Income"
@

@@

estv_masse <- estv %>% 
  filter(kanton=="CH",
         eink_art=="Nach steuerbarem Einkommen",
         fall=="Normalfälle",
         anz_pflichtige>0) %>%
        # steuerperiode!=1945.5) %>% 
  select(bemessungsjahre, steink, kanton, eink_ll, eink_ul,anz_pflichtige) %>%
  group_by(factor(bemessungsjahre)) %>%
  mutate(mean_steink=steink/anz_pflichtige) %>%
  summarise(Gini=gini(mean_steink,weights=anz_pflichtige),Atkinson=getAtkinson(mean_steink,w=anz_pflichtige),Theil=getTheil(mean_steink,w=anz_pflichtige))
estv_masse$id<-1
names(estv_masse)<-c("Year","Gini","Atkinson","Theil","id")
estv_masse<-estv_masse[as.numeric(estv_masse$Year)>4,]
try(detach("package:reshape", unload=TRUE))
library(reshape2)
estv_masse_long <- melt(estv_masse,id=c("id","Year"))
